Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-28 WSSSPE1_report/WSSSPE1_summary_report.tex
fixing a bad cite

How work on scientific software is recognized and rewarded strongly
influences the motivation for particular kinds of work on scientific
software. A recurring theme of the panel discussion was that software
work in science is inadequately visible within the reputation system
underlying science; in other words it often doesn't ``count''. In his
paper for this workshop, Katz placed software work along with other
``activities that facilitate science but are not currently rewarded or
recognized''~\cite{Katz_WSSSPE}. Priem and Piwowar argued for the need
to ``support all researchers in presenting meaningful impact evidence
in tenure, promotion, and funding applications.''~\cite{Priem_WSSSPE}.
Knepley et al.~argued that the lack of visibility of software that
supported a piece of science ``can have detrimental effects on
funding, future library development, and even scientific
careers.''~\cite{Knepley_WSSSPE}.

>>>>

How work on scientific software is recognized and rewarded strongly
influences the motivation for particular kinds of work on scientific
software. A recurring theme of the panel discussion was that software
work in science is inadequately visible within the reputation system
underlying science; in other words it often doesn't ``count''. In his
paper for this workshop, Katz placed software work along with other
``activities that facilitate science but are not currently rewarded or
recognized''~\cite{Katz2_WSSSPE}. Priem and Piwowar argued for the need
to ``support all researchers in presenting meaningful impact evidence
in tenure, promotion, and funding applications.''~\cite{Priem_WSSSPE}.
Knepley et al.~argued that the lack of visibility of software that
supported a piece of science ``can have detrimental effects on
funding, future library development, and even scientific
careers.''~\cite{Knepley_WSSSPE}.
